```{r, echo=FALSE, comment=NA, strip.white=FALSE} 
## Randomizing resume features
## The Limited Reach of State Ideology in China: Experimental Evidence from China's Labor Market
## Jennifer Pan and Tongtong Zhang
## Updated: December 3, 2017

## Description: third blank resume template (format C)
######################################################################################
```
---
title: ''
author: ''
date: ''
output:
  word_document:
    reference_docx: CV-format3.docx
  pdf_document: default
  html_document: default
---
```{r, echo=FALSE, comment=NA, strip.white=FALSE} 
#knitr::opts_chunk$set(opts.label="kill_prefix")
#rm(list=ls())
#setwd("/Users/tongtongzhang/Dropbox (IPL)/Job experiment/CV/Conjoint CV")
#majors<-read.csv("majors.csv",header=TRUE, stringsAsFactors = FALSE,sep=",")
#internships<-read.csv("internships.csv",header=TRUE, stringsAsFactors = FALSE,sep="\t")
#allegiance_treatment<-read.csv("allegiance_treatment.csv",header=TRUE, stringsAsFactors = FALSE,sep="\t")
#extra2nd<-read.csv("2nd_extracurricular.csv",header=TRUE, stringsAsFactors = FALSE,sep=",")

#setwd("/Users/tongtongzhang/Dropbox (IPL)/Job experiment/Implementation/STEP4_Application log/Randomization_result")
#data<-read.csv("randomization1121.csv",header=TRUE, stringsAsFactors = FALSE,sep=",")
#d<-data[data$format==1,]
#i<-1
name<-d[i,"name"]
gender<-d[i,"gender"]
phonenumber<-d[i,"phonenumber"]
email<-d[i,"sender_email"]

university<-d[i,"university"]
block<-d[i,"block"]
major_number<-d[i,"major"]
major<-majors[majors$block==block & majors$major_number==major_number, "major"]
direction<-majors[majors$block==block & majors$major_number==major_number, "direction"]
cohort_rank<-d[i,"cohort_rank"]


intern1_number<-d[i,"intern1"]
intern2_number<-d[i,"intern2"]
intern1_org<-internships[internships$block==block & internships$intern_number==intern1_number, "intern_org"]
intern1_bullet1<-internships[internships$block==block & internships$intern_number==intern1_number, "intern_bullet1"]
intern1_bullet2<-internships[internships$block==block & internships$intern_number==intern1_number, "intern_bullet2"]
intern2_org<-internships[internships$block==block & internships$intern_number==intern2_number, "intern_org"]
intern2_bullet1<-internships[internships$block==block & internships$intern_number==intern2_number, "intern_bullet1"]
intern2_bullet2<-internships[internships$block==block & internships$intern_number==intern2_number, "intern_bullet2"]

allegiance<-d[i,"allegiance"]
gradation<-d[i,"gradation"]
allegiance_org<-allegiance_treatment[allegiance_treatment$allegiance==allegiance & allegiance_treatment$gradation==gradation, "org"]
allegiance_bullet<-allegiance_treatment[allegiance_treatment$allegiance==allegiance & allegiance_treatment$gradation==gradation, "gradation_wording"]
#"每周组织一次讨论会，分享阅读中国特色社会主义理论著作的感受。  \n#####-通过研究会的活动，我感到只有中国特色社会主义才能发展中国。  "

extra2<-d[i,"extra2"]
extra2_org<-extra2nd[extra2,"org"]
extra2_bullet1<-extra2nd[extra2,"bullet1"]
extra2_bullet2<-extra2nd[extra2,"bullet2"]
  
certificates<-sample(c("普通话二级甲等",d[i,"certificate1"],d[i,"certificate2"]),3,FALSE)
certificate1<-certificates[1]
certificate2<-certificates[2]
certificate3<-certificates[3]

computer<-sample(c("Java","Photoshop","MS Office",d[i,"computer"]),4,FALSE)
CCP<-d[i,"ccp"]
hobbies<-c(d[i,"hobby1"],d[i,"hobby2"])
```
#`r as.name(as.character(name))`  
##性别：`r as.name(as.character(gender))`  
##电话：`r as.name(as.character(phonenumber))` 
##电子邮箱：`r as.name(as.character(email))`  
*********  
  
###教育背景  
####2014.9-至今  &nbsp; &nbsp; &nbsp;&nbsp;&nbsp; &nbsp;&nbsp; &nbsp;&nbsp; **`r as.name(as.character(university))`** &nbsp; &nbsp; &nbsp;&nbsp; `r as.name(as.character(major))` &nbsp; &nbsp; &nbsp;&nbsp; 硕士在读  
#####主修方向：`r as.name(as.character(direction))` &nbsp;&nbsp;   

&nbsp; &nbsp; &nbsp;  
  
####2010.9-2014.7  &nbsp; &nbsp; &nbsp;&nbsp; &nbsp; &nbsp; **`r as.name(as.character(university))`** &nbsp; &nbsp; &nbsp;&nbsp; `r as.name(as.character(major))` &nbsp; &nbsp; &nbsp;&nbsp; 学士  
#####专业绩点排名：前`r as.name(as.character(cohort_rank))` &nbsp;&nbsp;    

&nbsp; &nbsp; &nbsp;  
  
###实习经历  
####2016.7-2016.8  &nbsp; &nbsp; &nbsp;&nbsp; &nbsp; &nbsp; **`r as.name(as.character(intern1_org))`**   
#####-`r as.name(as.character(intern1_bullet1))`。  
#####-`r as.name(as.character(intern1_bullet2))`。 

&nbsp; &nbsp; &nbsp;  
  
####2015.7-2015.8  &nbsp; &nbsp; &nbsp;&nbsp; &nbsp; &nbsp; **`r as.name(as.character(intern2_org))`**  
#####-`r as.name(as.character(intern2_bullet1))`。    
#####-`r as.name(as.character(intern2_bullet2))`。 

&nbsp; &nbsp; &nbsp;  
  
###校园经历  
####2012.9-至今  &nbsp; &nbsp; &nbsp;&nbsp;&nbsp; &nbsp;&nbsp; &nbsp;&nbsp; **`r as.name(as.character(university))``r as.name(as.character(allegiance_org))`** &nbsp; &nbsp; &nbsp;&nbsp;    
#####-`r as.name(as.character(allegiance_bullet))`    
  
&nbsp; &nbsp; &nbsp;  
  
####2010.9-2012.7  &nbsp; &nbsp; &nbsp;&nbsp; &nbsp; &nbsp; **`r as.name(as.character(university))``r as.name(as.character(extra2_org))`** &nbsp; &nbsp;      
#####-`r as.name(as.character(extra2_bullet1))`。  
#####-`r as.name(as.character(extra2_bullet2))`。   

&nbsp; &nbsp; &nbsp;  
  
###荣誉与证书  
####2014   &nbsp; &nbsp; &nbsp;&nbsp;&nbsp; &nbsp;&nbsp; &nbsp;&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;&nbsp; `r as.name(as.character(certificate1))` &nbsp; &nbsp; &nbsp;&nbsp;    
####2013  &nbsp; &nbsp; &nbsp;&nbsp;&nbsp; &nbsp;&nbsp; &nbsp;&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; &nbsp;&nbsp; &nbsp;&nbsp;`r as.name(as.character(certificate2))` &nbsp; &nbsp; &nbsp;&nbsp;    
####2012  &nbsp; &nbsp; &nbsp;&nbsp;&nbsp; &nbsp;&nbsp; &nbsp;&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; &nbsp;&nbsp; &nbsp;&nbsp;`r as.name(as.character(certificate3))` &nbsp; &nbsp; &nbsp;&nbsp;  

&nbsp; &nbsp; &nbsp;  
  
###个人技能
####英语：大学英语六级  
####计算机：`r paste(as.name(as.character(computer[1])), ",", as.name(as.character(computer[2])),",", as.name(as.character(computer[3])), ",", as.name(as.character(computer[4])))`&nbsp; &nbsp;   
####政治面貌：`r as.name(as.character(CCP))`&nbsp; &nbsp;   
####兴趣爱好：`r paste(as.name(as.character(hobbies[1])), ",", as.name(as.character(hobbies[2])))`  

```{r, echo=FALSE, comment=NA, strip.white=FALSE} 
#knitr::opts_chunk$set(opts.label="kill_prefix")
name<-d[i,"name_eng"]
gender<-d[i,"gender_eng"]
phonenumber<-d[i,"phonenumber"]
email<-d[i,"sender_email"]

university<-d[i,"university_eng"]
block<-d[i,"block"]
major_number<-d[i,"major"]
major<-majors[majors$block==block & majors$major_number==major_number, "major_eng"]
direction<-majors[majors$block==block & majors$major_number==major_number, "direction_eng"]
cohort_rank<-d[i,"cohort_rank"]


intern1_number<-d[i,"intern1"]
intern2_number<-d[i,"intern2"]
intern1_org<-internships[internships$block==block & internships$intern_number==intern1_number, "intern_org_eng"]
intern1_bullet1<-internships[internships$block==block & internships$intern_number==intern1_number, "intern_bullet1_eng"]
intern1_bullet2<-internships[internships$block==block & internships$intern_number==intern1_number, "intern_bullet2_eng"]
intern2_org<-internships[internships$block==block & internships$intern_number==intern2_number, "intern_org_eng"]
intern2_bullet1<-internships[internships$block==block & internships$intern_number==intern2_number, "intern_bullet1_eng"]
intern2_bullet2<-internships[internships$block==block & internships$intern_number==intern2_number, "intern_bullet2_eng"]

allegiance<-d[i,"allegiance"]
gradation<-d[i,"gradation"]
allegiance_org<-allegiance_treatment[allegiance_treatment$allegiance==allegiance & allegiance_treatment$gradation==gradation, "org_eng"]
allegiance_bullet<-allegiance_treatment[allegiance_treatment$allegiance==allegiance & allegiance_treatment$gradation==gradation, "gradation_wording_eng"]

extra2<-d[i,"extra2"]
extra2_org<-extra2nd[extra2,"org_eng"]
extra2_bullet1<-extra2nd[extra2,"bullet1_eng"]
extra2_bullet2<-extra2nd[extra2,"bullet2_eng"]

certificates[which(certificates=="普通话二级甲等")]<-"Mandarin secondary-level A certificate"
certificates[which(certificates==d[i,"certificate1"])]<-d[i,"certificate1_eng"]
certificates[which(certificates==d[i,"certificate2"])]<-d[i,"certificate2_eng"]
certificate1<-certificates[1]
certificate2<-certificates[2]
certificate3<-certificates[3]

#computer<-sample(c("Java","Photoshop","MS Office",d[i,"computer"]),4,FALSE)
CCP<-d[i,"ccp_eng"]
hobbies<-c(d[i,"hobby1_eng"],d[i,"hobby2_eng"])
```

  
  
  
&nbsp; &nbsp; &nbsp;  
  
&nbsp; &nbsp; &nbsp;  

&nbsp; &nbsp; &nbsp;  
   
#`r as.name(as.character(name))`  
##Gender：`r as.name(as.character(gender))`  
##Phone number：`r as.name(as.character(phonenumber))` 
##Email：`r as.name(as.character(email))`  
*********  
  
###Education  
####2014.9-present  &nbsp; &nbsp; &nbsp;&nbsp;&nbsp; &nbsp; **`r as.name(as.character(university))`** &nbsp; &nbsp;&nbsp;&nbsp; Master in progress
##### &nbsp; Major: `r as.name(as.character(major))`&nbsp;&nbsp;      
##### &nbsp; Concentration: `r as.name(as.character(direction))` &nbsp;&nbsp;  
&nbsp; &nbsp; &nbsp;  
  
####2010.9-2014.7  &nbsp; &nbsp; &nbsp;&nbsp; &nbsp; &nbsp; **`r as.name(as.character(university))`** &nbsp; &nbsp; &nbsp;&nbsp; Bachelor  
##### &nbsp; Major: `r as.name(as.character(major))`&nbsp; &nbsp;  
##### &nbsp; Cohort GPA ranking：Top&nbsp;`r as.name(as.character(cohort_rank))` &nbsp;&nbsp; 
&nbsp; &nbsp; &nbsp;  
  
###Internship Experience  
####2016.7-2016.8  &nbsp; &nbsp; &nbsp;&nbsp; &nbsp; &nbsp; **`r as.name(as.character(intern1_org))`**   
#####-`r as.name(as.character(intern1_bullet1))`.  
#####-`r as.name(as.character(intern1_bullet2))`.  

&nbsp; &nbsp; &nbsp;  
  
####2015.7-2015.8  &nbsp; &nbsp; &nbsp;&nbsp; &nbsp; &nbsp; **`r as.name(as.character(intern2_org))`**  
#####-`r as.name(as.character(intern2_bullet1))`.    
#####-`r as.name(as.character(intern2_bullet2))`.     

&nbsp; &nbsp; &nbsp;  
  
###Extracurricular Activities  
####2012.9-present  &nbsp; &nbsp; &nbsp;&nbsp;&nbsp; &nbsp; **`r as.name(as.character(allegiance_org))`** &nbsp; &nbsp; &nbsp;&nbsp;    
#####-`r as.name(as.character(allegiance_bullet))`  
  
&nbsp; &nbsp; &nbsp;  
  
####2010.9-2012.7  &nbsp; &nbsp; &nbsp;&nbsp; &nbsp; &nbsp; **`r as.name(as.character(extra2_org))`** &nbsp; &nbsp;      
#####-`r as.name(as.character(extra2_bullet1))`.      
#####-`r as.name(as.character(extra2_bullet2))`.     

&nbsp; &nbsp; &nbsp;  
  
###Awards and Certificates  
####2014   &nbsp; &nbsp; &nbsp;&nbsp;&nbsp; &nbsp;&nbsp; &nbsp;&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;&nbsp; `r as.name(as.character(certificate1))` &nbsp; &nbsp; &nbsp;&nbsp;    
####2013  &nbsp; &nbsp; &nbsp;&nbsp;&nbsp; &nbsp;&nbsp; &nbsp;&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; &nbsp;&nbsp; &nbsp;&nbsp;`r as.name(as.character(certificate2))` &nbsp; &nbsp; &nbsp;&nbsp;    
####2012  &nbsp; &nbsp; &nbsp;&nbsp;&nbsp; &nbsp;&nbsp; &nbsp;&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; &nbsp;&nbsp; &nbsp;&nbsp;`r as.name(as.character(certificate3))` &nbsp; &nbsp; &nbsp;&nbsp;  

&nbsp; &nbsp; &nbsp;  
  
###Personal Skills  
####English: CET-6  
####Computer skills: `r paste(as.name(as.character(computer[1])), ",", as.name(as.character(computer[2])),",", as.name(as.character(computer[3])), ",", as.name(as.character(computer[4])))`&nbsp; &nbsp;   
####Political affiliation: `r as.name(as.character(CCP))`&nbsp; &nbsp;   
####Hobbies: `r paste(as.name(as.character(hobbies[1])), ",", as.name(as.character(hobbies[2])))` 